---
title: "Main Results"
output:
  word_document: default
  pdf_document: 
    keep_tex: yes
  html_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(dpi = 1200)
knitr::opts_chunk$set(fig.width=6)
library(tidyverse)
library(broom)
library(knitr)
library(extrafont)
library(ggstar)
extrafont::loadfonts(quiet = TRUE)
```


```{r}
if (file.exists("data/results-summary.RData")) {
  load("data/results-summary.RData")
} else {
  load("data/gmethods_ppmi_pdmedyn.RData")
  load("data/gmethods_ppmi_onldopa.RData")
  
  change_names <- function(df) { df %>% 
      separate(outcome,c("Outcome","Year"),sep = "_year") %>% unite("Model", method, modelname) 
  }
  summ_stats <- function(df) { df %>% group_by(Outcome,Model,Year,form,term) %>%
    summarize(est=mean(estimate,na.rm=TRUE),sd=sd(estimate,na.rm=TRUE),n=n()) %>% ungroup }
  
  bs_pdmedyn_all <- bs_results_PDMEDYN_all  %>% change_names %>% summ_stats
  bs_pdmedyn_started <-  bs_results_PDMEDYN_medication  %>% change_names %>% summ_stats
  bs_onldopa_all <- bs_results_onldopa_all  %>% change_names %>% summ_stats
  bs_onldopa_started <-  bs_results_onldopa_medication  %>% change_names %>% summ_stats
  bs_onldopa_levoonly <-  bs_results_onldopa_levoonly  %>% change_names %>% summ_stats
  
  
  full_results_PDMEDYN <- full_results_PDMEDYN_all %>% change_names
  full_results_PDMEDYN_started <- full_results_PDMEDYN_medication %>% change_names
  full_results_onldopa <- full_results_onldopa_all %>% change_names
  full_results_onldopa_started <- full_results_onldopa_medication %>% change_names
  full_results_onldopa_levoonly <- full_results_onldopa_levoonly %>% change_names
  
  
  bs_pdmedyn_extra <- bs_pdmedyn_started
  full_results_PDMEDYN_extra <- full_results_PDMEDYN_started
  load("data/gmethods_ppmi_pdmedyn_restricted.RData")

  bs_pdmedyn_started <- bind_rows(
    bs_results_PDMEDYN_y2 %>% filter(str_detect(outcome,"_year2")),
    bs_results_PDMEDYN_y3 %>% filter(str_detect(outcome,"_year3")),
    bs_results_PDMEDYN_y4 %>% filter(str_detect(outcome,"_year4"))
  ) %>% change_names %>% summ_stats
  
  full_results_PDMEDYN_started <- bind_rows(
    full_results_PDMEDYN_y2 %>% filter(str_detect(outcome,"_year2")),
    full_results_PDMEDYN_y3 %>% filter(str_detect(outcome,"_year3")),
    full_results_PDMEDYN_y4 %>% filter(str_detect(outcome,"_year4"))
  )%>% change_names
  
  load("data/gmethods_ppmi_onldopa_restricted.RData")
  
  bs_onldopa_levoonly <- bind_rows(
    bs_results_onldopa_levoonly_y2 %>% filter(str_detect(outcome,"_year2")),
    bs_results_onldopa_levoonly_y3 %>% filter(str_detect(outcome,"_year3")),
    bs_results_onldopa_levoonly_y4 %>% filter(str_detect(outcome,"_year4"))
  ) %>% change_names %>% summ_stats
  
  full_results_onldopa_levoonly <- bind_rows(
    full_results_onldopa_levoonly_y2 %>% filter(str_detect(outcome,"_year2")),
    full_results_onldopa_levoonly_y3 %>% filter(str_detect(outcome,"_year3")),
    full_results_onldopa_levoonly_y4 %>% filter(str_detect(outcome,"_year4"))
  )%>% change_names
  
  
  
  save(full_results_PDMEDYN, full_results_PDMEDYN_started, full_results_PDMEDYN_extra, 
       bs_pdmedyn_all, bs_pdmedyn_started, bs_pdmedyn_extra,
       full_results_onldopa, full_results_onldopa_started, full_results_onldopa_levoonly,  
       bs_onldopa_all, bs_onldopa_levoonly, bs_onldopa_started,
       pats_stopped_PDMEDYN, pats_levoonly, pats_stopped_onldopa,
       file="data/results-summary.RData")
}
df_varying <- readRDS("data/df_varying.rds")
df_constant <- readRDS("data/df_constant.rds")
df_last <- readRDS("data/df_last.rds")

```

# Descriptive Statistics

## Patient characteristics

```{r}
lgperce_in_table <- function(x) {
  sprintf("%2.1f",mean(x,na.rm=TRUE)*100)
}

treat_length <- df_varying %>% 
  left_join(df_constant,by="id") %>% 
  group_by(id) %>% 
  summarize(years_treatment=sum(PDMEDYN)/2)


dbl_in_table <- function(x) {
  if (all(is.na(x))) {
    ""
  }
  else if (any(is.na(x))) {
    sprintf("%1.1f (%1.1f), NA:%d",mean(x,na.rm=TRUE), sd(x,na.rm=TRUE),sum(is.na(x)))
  } else {
   sprintf("%1.1f (%1.1f)",mean(x), sd(x))
  }
}

lg_in_table <- function(x) {
  sprintf("%1.2f",mean(x,na.rm=TRUE))
}


df_varying %>% 
  filter(!(id %in% c(pats_stopped_PDMEDYN))) %>% 
  left_join(df_constant,by="id") %>% 
  left_join(treat_length,by="id") %>% 
  filter(!is.na(years_treatment)) %>% 
  filter(years_treatment>0) %>% 
  filter(time==0) %>% 
  left_join(df_last %>% select(id,starts_with("LEDD")), by="id") %>% 
  #group_by(years_treatment) %>% 
  summarize(n=n(),
            `Age (Years)`=dbl_in_table(Age), 
            `Gender (% Men)`=lgperce_in_table(Sex=="Male"),
            `Education (Years)`=dbl_in_table(Education),
            `Disease Duration (Years)`=dbl_in_table(Duration),
            `MDS-UPDRS I`=dbl_in_table(MDS_UPDRS_I),
            `MDS-UPDRS II`=dbl_in_table(MDS_UPDRS_II),
            `MDS-UPDRS III`=dbl_in_table(MDS_UPDRS_III_other),
            MoCA=dbl_in_table(MoCA),
            `MSE-ADL`=dbl_in_table(MSEADLG),
            `SCOPA-AUT`=dbl_in_table(SCOPA_AUT),
            `QUIP (% any)`=lgperce_in_table(QUIP>0),
            `LEDD @ 2 years`=dbl_in_table(LEDD_year2),
            `LEDD @ 3 years`=dbl_in_table(LEDD_year3),
            `LEDD @ 4 years`=dbl_in_table(LEDD_year4),
            #`Treatment 0 years`=sum(years_treatment==0,na.rm=TRUE),
            `Treatment 0.5 years`=sum(years_treatment==0.5,na.rm=TRUE),
            `Treatment 1 year`=sum(years_treatment==1,na.rm=TRUE),
            `Treatment 1.5 years`=sum(years_treatment==1.5,na.rm=TRUE),
            `Treatment 2 years`=sum(years_treatment==2,na.rm=TRUE),
            #Censored=sum(is.na(years_treatment),na.rm=TRUE),
            ) %>% 
  gather("Variable","Value") %>% 
  #mutate(var=fct_inorder(var),
  #       years_treatment=fct_explicit_na(factor(years_treatment),na_level="Censored")) %>% 
  #spread(years_treatment,value) %>% 
  #rename(`Treatment Length`=var) %>% 
  kable(caption="Table 1: Baseline demographics and disease characteristics. Values are presented as mean (SD) unless stated otherwise. Montreal cognitive assessment scale (MoCA); Modified Schwab and England activities of daily living (MSE-ADL); Questionnaire for Impulsive-Compulsive Disorders in Parkinson’s Disease (QUIP); Levodopa Equivalent Daily Dose (LEDD). 
")
```

## Disease Progression
```{r dpi=1200, fig.width = 6, fig.cap='Figure 1: Average MDS-UPDRS III in OFF-state scores in the first four years, categorized by number of treatment years in the first two years of follow-up. Scores are obtained during biannual measurements until treatment initiation and annual measurements after treatment initiation.'}
df_plot <- readRDS("data/df_varying_all.rds") %>%  
  mutate(id=as.character(PATNO)) %>% 
  filter(time<9) %>% 
  #filter(!(id %in% my_ids)) %>% 
  left_join(df_constant,by="id") %>% 
  left_join(treat_length,by="id") %>% 
  mutate(MDS_UPDRS_III=if_else(time>(2-years_treatment)*2,as.numeric(MDS_UPDRS_III_off),MDS_UPDRS_III_other)) %>% 
  group_by(time, years_treatment) %>% 
  summarize(m=mean(MDS_UPDRS_III,na.rm=TRUE)) %>% 
  select(time,years_treatment,m) %>% 
  na.omit %>% 
  #filter(!(time %in% c(5,7))) %>%
  filter(!((time%%2==1) & time>(2-years_treatment)*2)) %>% 
  mutate(start=factor(2-years_treatment,levels=c(0,0.5,1,1.5,2),labels=c("t = 0","t = 0.5","t = 1","t = 1.5","t \u2265 2"))) %>% 
  mutate(moment=(time==2*(2-years_treatment)))

ggout <- df_plot %>% 
  ggplot(aes(x=time*6, y=m, group=factor(start), fill=factor(start), color=factor(start))) + 
  geom_point() + geom_line() + 
  geom_star(size=2, data=df_plot %>% filter(moment==TRUE, years_treatment!=0) %>% mutate(m=m-0.8+1.6*(years_treatment!=2)), inherit.aes = TRUE,show.legend = FALSE) + 
  scale_x_continuous(breaks =seq(0,48, by=6),expand=expand_scale(mult = 0.03, add = 0)) + theme_light()  + xlab("Month") + ylab("Average MDS-UPDRS Part III Score") + scale_color_viridis_d(name="Start PD medication") + scale_fill_viridis_d(name="Start PD medication") +
    theme(text=element_text(family="Lato"))
cairo_ps("figure/1.eps", width=6, height = 0.75*6)
print(ggout)
invisible(dev.off())
print(ggout)
```

```{r dpi=1200, fig.width = 6, fig.cap="Mean progression for the different treatment duration groups", eval=FALSE}
readRDS("data/df_varying_all.rds") %>%  
  mutate(id=as.character(PATNO)) %>% 
  filter(time<9) %>% 
  #filter(!(id %in% my_ids)) %>% 
  left_join(df_constant,by="id") %>% 
  left_join(treat_length,by="id") %>% 
  group_by(time,years_treatment) %>% 
  summarize(m=mean(MDS_UPDRS_I)) %>% 
  select(time,years_treatment,m) %>% 
  na.omit %>% 
  ggplot(aes(x=time*6,y=m,color=factor(years_treatment))) +geom_point() + geom_line() +
  scale_x_continuous(breaks =seq(0,48, by=6),expand=expand_scale(mult = 0.03, add = 0)) + theme_light()  + xlab("Month") + ylab("Average MDS-UPDRS Part I Score") + scale_color_viridis_d(name="Number of years of treatment") +theme(text=element_text(family="Lato"))
```


```{r}
process_results <- function(.x) {
  .x %>% 
    filter(term %in% c("I((treatment + treatment_lag1 + treatment_lag2 + treatment_lag3)/2)",
                       "I((treatment_lag1 + treatment_lag2 + treatment_lag3) * 2/3)")) %>% 
    filter(Model %in% c("Naive_msms","Naive_msms_adj","Censoring_msms_adj","IPW_msms_adj","gformula_msms_adj"))
}
```


# Confounding adjustment
```{r fig.asp=0.3, dpi=1200, fig.width = 8, fig.cap="Figure 2: Effect of an additional year of PD medication therapy on outcomes after two years in the subpopulation of patients that had started therapy at the time of measurement, estimated using different methods. For MDS-UPDRS, higher scores correspond to worse outcome, for Modified Schwab & England, lower scores correspond to worse outcomes. Adjusting for more of the (time-varying) confounding removes more of the spurious negative effects due to worse-off patients being more likely to start therapy early."}
plot_bootstrap <- function(df_res, df_boot) {
  df_boot_all <- df_boot %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"MDS-UPDRS Part I",
      Outcome=="MDS_UPDRS_II"~"MDS-UPDRS Part II",
      Outcome=="MDS_UPDRS_III_off"~"MDS-UPDRS Part III",
      Outcome=="MSEADLG"~"Modified Schwab & England"
    )) %>% 
    mutate(Model=case_when(
      Model=="Naive_msms"~"No Adjustment",
      Model=="Naive_msms_adj"~"Baseline Adjustment",
      Model=="Censoring_msms_adj"~"Baseline Adjustment + Censoring",
      Model=="IPW_msms_adj"~"Inverse Probability of Treatment Weighting",
      Model=="gformula_msms_adj"~"Parametric g-formula"
    ))
  
  df_res %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"MDS-UPDRS Part I",
      Outcome=="MDS_UPDRS_II"~"MDS-UPDRS Part II",
      Outcome=="MDS_UPDRS_III_off"~"MDS-UPDRS Part III",
      Outcome=="MSEADLG"~"Modified Schwab & England"
    )) %>% 
    mutate(Model=case_when(
      Model=="Naive_msms"~"No Adjustment",
      Model=="Naive_msms_adj"~"Baseline Adjustment",
      Model=="Censoring_msms_adj"~"Baseline Adjustment + Censoring",
      Model=="IPW_msms_adj"~"Inverse Probability of Treatment Weighting",
      Model=="gformula_msms_adj"~"Parametric g-formula"
    )) %>% 
    left_join(df_boot_all,by = c("Outcome", "Model", "Year")) %>%
    mutate(Outcome=fct_relevel(factor(Outcome),c("MDS-UPDRS Part III","Modified Schwab & England","MDS-UPDRS Part I"))) %>% 
    mutate(Model=fct_rev(fct_inorder(Model))) %>% 
    ggplot(aes(x=estimate,y=Model,color=Model)) +
    geom_vline(aes(xintercept=0))+
    geom_point() +
    geom_segment(aes(x=estimate-2*sd,xend=estimate+2*sd,yend=Model)) +
    theme_bw() +
    theme(text=element_text(family="sans"), 
          legend.position="none",
          panel.grid.major = element_line(linetype = 2,size=0.2),
          strip.background = element_rect(fill="white")) +
    ylab("") +xlab("") +
    facet_wrap(Outcome~.,labeller = function(.x) {label_value(.x,multi_line = FALSE)},ncol=3, scales = "free_x") +
    theme(strip.placement = "outside",text=element_text(family="Lato")) +
    NULL#coord_cartesian(xlim=c(-10,10))
}

ggout <- plot_bootstrap(
  full_results_PDMEDYN_started %>% process_results %>% filter(Year==2, Outcome %in% c("MDS_UPDRS_I","MDS_UPDRS_III_off","MSEADLG")),
  bs_pdmedyn_started %>% process_results %>% filter(Year==2, Outcome %in% c("MDS_UPDRS_I","MDS_UPDRS_III_off","MSEADLG"))
)

cairo_ps("figure/2.eps", width=8, height = 0.3*8)
print(ggout)
invisible(dev.off())
print(ggout)
```

# Main Outcomes

```{r fig.asp=0.4, dpi=1200, fig.width = 6, fig.cap="Figure 3: Effect of one year of PD medication treatment during the first two years of follow-up. Effect on MDS-UPDRS Part III subscore measured at year 2, 3 and 4, for inverse probability of treatment weighting and the parametric g-formula. Only patients who have started medication therapy at the time of the outcome measurement are included in the analysis."}
plot_bootstrap_compact <- function(df_res, df_boot) {
  df_res <- df_res %>% mutate(dataset=fct_inorder(dataset))
  df_boot <- df_boot %>% mutate(dataset=fct_inorder(dataset))
  
  df_boot_all <- df_boot %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"Part I",
      Outcome=="MDS_UPDRS_II"~"Part II",
      Outcome=="MDS_UPDRS_III_other"~"Part 3",
      Outcome=="MDS_UPDRS_III_off"~"MDS-UPDRS Part III"
    )) %>% 
    mutate(Model=case_when(
      Model=="IPW_msms_adj"~"Inverse Probability of Treatment Weighting",
      Model=="gformula_msms_adj"~"Parametric g-formula"
    ))
  
  df_res %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"Part I",
      Outcome=="MDS_UPDRS_II"~"Part II",
      Outcome=="MDS_UPDRS_III_other"~"Part 3",
      Outcome=="MDS_UPDRS_III_off"~"MDS-UPDRS Part III"
    )) %>% 
    mutate(Model=case_when(
      Model=="IPW_msms_adj"~"Inverse Probability of Treatment Weighting",
      Model=="gformula_msms_adj"~"Parametric g-formula"
    )) %>% 
    filter(Outcome=="MDS-UPDRS Part III") %>% 
    left_join(df_boot_all,by = c("Outcome", "Model", "Year","dataset")) %>% 
    mutate(Model=fct_rev(fct_inorder(Model))) %>% 
    ggplot(aes(y=fct_rev(Year),x=estimate,color=Model,shape=Model)) +
    geom_vline(aes(xintercept=0))+
    geom_point(position=position_dodge(.5),size=2) +
    #geom_pointrange(aes(ymin=estimate-2*sd,ymax=estimate+2*sd),position=position_dodge(.5)) +
    geom_errorbarh(aes(xmin=estimate-2*sd,xmax=estimate+2*sd),position=position_dodge(.5),height=0) +
    scale_x_continuous(breaks=seq(-20,10,by=5)) +
    coord_cartesian(xlim=c(-22,10)) +
    theme_bw() +
    theme(text=element_text(family="Lato"), 
          legend.position="bottom",
          panel.grid.major = element_line(linetype = 2,size=0.2),
          panel.grid.minor = element_line(linetype = 2,size=0.2),
          strip.background = element_rect(fill="white")) +
    xlab("") +ylab("Year") +
    facet_grid(Outcome~dataset,labeller = function(.x) {label_value(.x,multi_line = FALSE)}) +
    #scale_color_viridis_d(option = "E",end=0.8) +
    theme(strip.placement = "outside") +
    guides(linetype=NULL, shape=guide_legend(reverse=TRUE,title=NULL), color=guide_legend(reverse=TRUE,title=NULL)) +
    #scale_color_viridis_d() +
    NULL#coord_cartesian(xlim=c(-10,10))
}

ggout <- plot_bootstrap_compact(
  bind_rows(full_results_PDMEDYN_started %>% process_results %>% mutate(dataset="PD Medication"), 
            full_results_onldopa_levoonly %>% process_results %>% mutate(dataset="Only Levodopa")) %>% 
    filter(Model %in% c("IPW_msms_adj","gformula_msms_adj"), str_detect(Outcome,"MDS_UPDRS")),
  bind_rows(bs_pdmedyn_started %>% process_results %>% mutate(dataset="PD Medication"),
            bs_onldopa_levoonly %>% process_results %>% mutate(dataset="Only Levodopa")) %>% 
    filter(Model %in% c("IPW_msms_adj","gformula_msms_adj"), str_detect(Outcome,"MDS_UPDRS"))
) + theme(strip.text.y = element_text(family="Lato",size=8) )
print(ggout)

cairo_ps("figure/3.eps", width=6, height = 0.4*6)
print(ggout)
invisible(dev.off())

```

In the table below: obs refers to the number of non-missing measurements used for the esitmation for the IPTW models, and to the number of simulated outcomes for the g-formula (4 treatment options times 100 simulations per patient for the year 2 outcomes and 5 treatment options times 100 simulations per patient for the other outcomes). 
```{r}
calc_table <- function(df_res, df_boot) {
  df_res <- df_res %>% mutate(dataset=fct_inorder(dataset))
  df_boot <- df_boot %>% mutate(dataset=fct_inorder(dataset))
  
  df_boot_all <- df_boot %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"Part I",
      Outcome=="MDS_UPDRS_II"~"Part II",
      Outcome=="MDS_UPDRS_III_other"~"Part 3",
      Outcome=="MDS_UPDRS_III_off"~"Part III"
    )) %>% 
    mutate(Model=case_when(
      Model=="IPW_msms_adj"~"Inverse Probability Weighting",
      Model=="gformula_msms_adj"~"g-formula"
    ))
  
  df_res %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"Part I",
      Outcome=="MDS_UPDRS_II"~"Part II",
      Outcome=="MDS_UPDRS_III_other"~"Part 3",
      Outcome=="MDS_UPDRS_III_off"~"Part III"
    )) %>% 
    mutate(Model=case_when(
      Model=="IPW_msms_adj"~"Inverse Probability Weighting",
      Model=="gformula_msms_adj"~"g-formula"
    )) %>% 
    filter(Outcome=="Part III") %>% 
    left_join(df_boot_all,by = c("Outcome", "Model", "Year","dataset")) %>% 
    mutate(Model=fct_rev(fct_inorder(Model))) %>% 
    mutate(CI=paste0("(",round(estimate-1.96*sd,2)," - ",round(estimate+1.96*sd,2),")"))
}

calc_table(
  bind_rows(full_results_PDMEDYN_started %>% process_results %>% mutate(dataset="PD Medication")) %>% 
    filter(Model %in% c("IPW_msms_adj","gformula_msms_adj"), str_detect(Outcome,"MDS_UPDRS")),
  bind_rows(bs_pdmedyn_started %>% process_results %>% mutate(dataset="PD Medication")) %>% 
    filter(Model %in% c("IPW_msms_adj","gformula_msms_adj"), str_detect(Outcome,"MDS_UPDRS"))
) %>% select(Model, Year, estimate, CI, obs)  %>% kable(digits=2)
```


# Auxiliary outcomes

```{r message=FALSE, dpi=1200, fig.width = 9, fig.asp=0.3, fig.cap="Figure 4: Effect of one year of PD medication treatment during the first two years of follow-up. Effect on auxiliary outcomes at year 2, 3 and 4 for inverse probability of treatment weighting. Only patients who have started medication therapy at the time of the outcome measurement are included in the analysis."}
plot_bootstrap_aux <- function(df_res, df_boot) {
  df_boot_all <- df_boot %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"MDS UPDRS Part I",
      Outcome=="MDS_UPDRS_II"~"MDS UPDRS Part II",
      Outcome=="MSEADLG"~"Mod. Schwab & England",
      Outcome=="NP4OFF"~"Motor fluctuations",
      Outcome=="NP4WDYSK"~"Presence of dyskinesias",
      Outcome=="SCOPA_AUT"~"SCOPA-AUT",
      TRUE~Outcome
    ))
  
  df_res %>% 
    mutate(Outcome=case_when(
      Outcome=="MDS_UPDRS_I"~"MDS UPDRS Part I",
      Outcome=="MDS_UPDRS_II"~"MDS UPDRS Part II",
      Outcome=="MSEADLG"~"Mod. Schwab & England",
      Outcome=="NP4OFF"~"Motor fluctuations",
      Outcome=="NP4WDYSK"~"Presence of dyskinesias",
      Outcome=="SCOPA_AUT"~"SCOPA-AUT",
      TRUE~Outcome
    )) %>% 
    
    left_join(df_boot_all,by = c("Outcome", "Model", "Year","dataset")) %>% 
    #filter(!(Outcome %in% c("MDS UPDRS Part I","MDS UPDRS Part II"))) %>% 
    mutate(Model=fct_rev(fct_inorder(Model))) %>% 
    mutate(Outcome=fct_inorder(Outcome)) %>% 
    mutate(Outcome=fct_relevel(Outcome,"SCOPA-AUT",after=4)) %>% 
    mutate(dataset=fct_inorder(dataset)) %>% 
    ggplot(aes(x=estimate,y=fct_rev(Year)),color="blue") +
    geom_vline(aes(xintercept=0))+
    geom_point() +
    geom_segment(aes(x=estimate-2*sd,xend=estimate+2*sd,yend=Year),alpha=0.6) +
    theme_bw() +
    theme(text=element_text(family="Lato"), 
          legend.position="none",
          panel.spacing.x=unit(0.3,"cm"),
          panel.grid.major = element_line(linetype = 2,size=0.2),
          panel.grid.minor = element_line(linetype = 2,size=0.2),
          strip.background = element_rect(fill="white"),
          strip.text = element_text(size=7)) +
    ylab("") +xlab("") +
    facet_grid(dataset~Outcome, scales="free_x") +
    scale_x_continuous(expand=expansion(mult=0.1),breaks=scales::breaks_pretty(n=4)) +
    #facet_wrap(Outcome~dataset,labeller = function(.x) {label_value(.x,multi_line = TRUE)},scales="free_x",ncol=2) +
    theme(strip.placement = "outside") +
    NULL#coord_cartesian(xlim=c(-10,10))
}

process_results_aux <- function(.x) {
  .x %>% 
    filter(term %in% c("I((treatment + treatment_lag1 + treatment_lag2 + treatment_lag3)/2)",
                       "I((treatment_lag1 + treatment_lag2 + treatment_lag3) * 2/3)")) %>% 
    mutate(form2=case_when(
      str_detect(form,"Age") ~ "interact",
      str_detect(form,"\\) +") ~ "Adjust",
      str_detect(form,"treatment_lag3\\)/") ~ "Naive",
      TRUE ~ "other")
    ) %>% 
    filter(Model %in% c("IPW_msms","IPW_msms_adj"))  %>%
    filter(Outcome %in% c("MDS_UPDRS_I","MDS_UPDRS_II","NP4WDYSK","NP4OFF","MSEADLG","MoCA","SCOPA_AUT")) %>% 
    group_by(Outcome,Year) %>% arrange(desc(Model)) %>% slice(1) %>% ungroup # Select adjusted if available
}

ggout <- plot_bootstrap_aux(
  bind_rows(full_results_PDMEDYN_started %>% process_results_aux %>% mutate(dataset="PD Medication"), 
            full_results_onldopa_levoonly %>% process_results_aux %>% mutate(dataset="Levodopa Only")),
  bind_rows(bs_pdmedyn_started %>% process_results_aux %>% mutate(dataset="PD Medication"),
            bs_onldopa_levoonly %>% process_results_aux %>% mutate(dataset="Levodopa Only"))
) + ylab("Year")

cairo_ps("figure/4.eps", width=9, height = 0.3*8)
print(ggout)
invisible(dev.off())
print(ggout)
```
